The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete

### 2014-01-14 main/s_level_2.tex
made one file for LICS

\newcommand\alt{\underline}

@@

\begin{lemma}
If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
\end{lemma}

@@

	\item
Finally, to permutate edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
%
Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to permute $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
%
Perform a second permutation to return $d_0$ and $d_1$ their proper edge-absorbers.

@@

\begin{lemma}
If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then $\itn\gamma\sim\itn\delta$.
\end{lemma}

>>>>

@@

\begin{lemma}
\label{lem:permute edge-absorbers}
If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
\end{lemma}

@@

	\item
Finally, to permute edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
%
Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to permute $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
%
A second such exchange is needed to re-attach $d_0$ and $d_1$ to their original targets.

@@

Let $\itn\gamma'$ be $\itn\gamma$ where the first two edge-absorbers are exchanged.

\begin{lemma}
If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\sim\itn\delta$ or $\itn\gamma\sim\itn\delta'$.
\end{lemma}

\begin{proof}
We will prove the case where $\gamma\sim\delta$ is a single reconfiguration step; the general case follows because the proof goes through also when $\itn\gamma'$ replaces $\itn\gamma$ in the statement of the lemma.
%
Let $\gamma$ and $\delta$ agree on every edge except $e$, where $\gamma(e)=v$ and $\delta(e)=w$.
%
Firstly, using Lemma~\ref{lem:octopus roll}, for the edges $d$ other than $e$ such that $\gamma(d)=v$, the weight elements of the edge-gadgets $\itn d$ may be linked to the constraint elements of $\itn v$, in accordance with the target configuration $\itn\delta$.
%
Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is free.
%
Next, the indicator vertex of $\itn e$, which links to the indicator of $\itn v$, is re-attached to the indicator of $\itn w$.
%
Again using Lemma~\ref{lem:octopus roll}, the weight elements of edge-gadgets connected to $\itn w$, including $\itn e$, may be linked in accordance with $\itn\delta$.
%
The resulting proof net is $\itn\delta$ modulo a permutation of edge-absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute edge-absorbers}.
\end{proof}
